
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Dong Qichen} % Your name
\address{22 Oregon Close, Manchester, UK, M13 9SA} % Your address
\address{(+44) 742-250-7895 \\ qichen.dong@cern.ch} % Your phone number and email
\begin{document}

    \begin{rSection}{Education}
        {\bf University of Manchester, UK} \hfill {\bf September 2020 - Present} 
        \\ PhD Student in High Energy Physics\hfill
        \\ Expected December 2024 
        \\[0pt]
        \ \\[0pt]
        {\bf University of Manchester, UK} \hfill {\bf September 2018 - June 2020} 
        \\ Master of Physics \hfill { Average GPA: 71.4 }
        \\ Relevant courses: Quantum field theory, Gravitation, Frontier of particle physics
        \\[0pt]
        \ \\[0pt]
        {\bf Shandong University, China} \hfill {\bf September 2015 - June 2018} 
        \\ Bachelor of Science in Physics.\hfill {  Overall GPA: 83.3 }
    \end{rSection}

    \begin{rSection}{Research Experience}
        {\bf ATLAS Qualification Project} \hfill {\bf January 2021 - Present}\\
        {\bf \em CP Violation in Vector Boson Scattering (VBS) Process}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   Project supervised by Prof. Terry Wyatt.
            \item   Developing an improved method to identify the pair production of the heaviest lepton in the ATLAS experiment in the Large Hadron Collider.
            \item   The new method will be published for the benefit of the ATLAS collaboration.
        \end{enumerate}
        \ \\[0pt]
        {\bf MPhys Project} \hfill {\bf September 2019 - June 2020}\\
        {\bf \em CP Violation in Vector Boson Scattering (VBS) Process}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   Project supervised by Prof. Andrew Pilkington.
            \item   Marked 81\%.
            \item   Searching for extra source of CP violation which contributes to the large matter anti-matter asymmetry 
                    in the universe.
            \item   carefully searching for the extremely rare pure electro-weak VBS process using $139 fb^{-1}$ 
                    of collision data accumulated in recent years at Atlas detector.
            \item   Events in a VBS enhanced phase space were reconstructed and unfolded to remove inefficiency and resolution of the detector, 
                    so that the measured data can be used to set limit to new physics model.
            \item   Observables potentially sensitive to CP violation are being studied now.
        \end{enumerate}
        \ \\[0pt]
        {\bf  Laboratory} \hfill {\bf November 2018 - January 2019}\\
        {\bf \em Measurement of CP Violation in $B^{\pm}\rightarrow\pi^{\pm}\pi^{+}\pi^{-}$ Channel}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   Third laboratory project supervised by Dr. Marco Gersabeck and Dr. Fedor Bezrukov, marked 90\% report and 76\% overall.
            \item   By reconstructing, selecting events and estimating background, evidence of inclusive 
                    CP violation in this channel by measuring difference between $B^{+}$ and $B^{-}$ events cross section was observed.
            \item   local CP violation in certain $m_{\pi^{+}\pi^{-}}$ phase spaces are observed.
        \end{enumerate}
        \ \\[0pt]
        {\bf Competition} \hfill {\bf September 2017}\\
        {\bf \em China Undergraduate Mathematical Contest in Modeling}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   A team of 3 students developing a mathematical model in 3 days to solve a problem of reconstructing and 
                    denoising CT images. 
            \item   Team leader and major contributor, first price in Shandong province of China.
        \end{enumerate}
        \ \\[0pt]
        {\bf Competition} \hfill {\bf June 2017 - September 2017}\\
        {\bf \em Shenzhen Cup Mathematical Modeling Competition}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   A team of 3 student work togethor in 3 months to model an open-ended real life problem, 
                    supervised by Professor Baodong Liu.
            \item   The relation between network quality and customer satisfaction in online video playback senario was studied.
            \item   relation between behavior of network transmition protocol in different network quality and variables selected 
                    to reflect user satisfaction were evaluated.
            \item   leader of the team and main contributor, reached the last 16 teams among China.
        \end{enumerate}

    \end{rSection}

    \begin{rSection}{Additional Experience}
        {\bf Voluntary Work} \hfill {\bf June 2016 - September 2017}\\
        {\bf \em Volunteer Teacher Supporting Primary Education in Remote Area}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   Group of first year students in the university volunteered to help primary school students who live in remote area in 
                    Sichuan province of China during summer break.
            \item   Achieved 120 hours of voluntary work and the team helped hundreds of children.
            \item   Local tobacco farming which can potentially reduce poverty was also investigated.
        \end{enumerate} 
        \ \\[0pt]
        {\bf Student Union Officer} \hfill {\bf September 2015 - June 2017}\\
        {\bf \em Officer and Minister of Voluntary Department of Shandong Student Union}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   Responsible for organising voluntary work hosted by the department.
            \item   Constructing and Managing a team of 20 undergraduate officers.
        \end{enumerate}
    \end{rSection}

    \begin{rSection}{Skills and Interests}
        \begin{description}
            \item[\bf Software: \ ] Proficient in programming with C/C++ and python; Using PhotoShop
            \item[\bf Language: ] Chinese(Native), English(Professional)
            \item[\bf Interests:\ \ ] Badminton, swimming, graphic design, programming
        \end{description} 
    \end{rSection}

    \begin{rSection}{Purpose of travel}
        \begin{enumerate}[leftmargin=*,label=$\bullet$]
            \item   Being a visiting student from the University of Manchester who is attched to CERN.
            \item   Visiting and contributing to the ATLAS experiment in Geneva,  which I have only been seeing virtually.
            \item   It is a dream for a PhD student in the field of particle physics to visit the LHC.  
        \end{enumerate} 
    \end{rSection}

\end{document}